Supplementary Information

### 2021-12-20 writing/appendix_a.Rmd
With RCS IVs for GLS models

---
title: "Supplementary Information"
short_title: COVID-19 Prescribing
bibliography:
- r-references.bib
- ../references/library.bib
output:
  pdf_document: default
  html_document:
    df_print: paged
ouput: html_document
---

```{r setup, include = FALSE}
## Packages
# devtools::install_github("w-hardy/serCymruTools")
library(plyr); library(dplyr)
library(rms)
library(nlme)
library(tidyverse)
library(lubridate)
library(tsibble)
library(fable)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(knitr)
library(kableExtra)
library(geepack)
library(papaja)
library(fuzzyjoin)
library(ggbiplot)

@@

## Data
gp <- 
  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid),
         hboard = case_when(hboard == "W11000023" ~ 
                              "Betsi Cadwaladr",
                            hboard == "W11000024" ~ 
                              "Powys",
                            hboard == "W11000025" ~ 
                              "Hywel Dda",
                            hboard == "W11000028" ~ 
                              "Aneurin Bevan",
                            hboard == "W11000029" ~ 
                              "Cardiff and Vale",
                            hboard == "W11000030" ~ 
                              "Cwm Taf Morgannwg",
                            hboard == "W11000031" ~ 
                              "Swansea Bay")) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  mutate(dispensing = case_when(tolower(dispensing) == "yes" ~ TRUE, 
                                tolower(dispensing) == "no" ~ FALSE),
         hboard = as.factor(hboard))

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data")) 
names(data_files) <- 
  str_remove_all(list.files("../data/prescribing_data"), ".rds")

@@

# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = FALSE, 
                      echo = FALSE, fig.pos = 'H')
kable_opts <- options(knitr.kable.NA = "-")
```

@@

```{r, gp-pca, fig.cap="Variance of QoF variables explained by individual principal components (lines) with cumulative proportion of variance explained (text)."}
#### Data ####
gp_2020 <- filter(gp, year == 2020)

@@

#### Analysis ####
gp_pca <- 
  prcomp(select(gp_2020, chd:flu), center = TRUE, scale. = TRUE)

plot(gp_pca, type = "lines", main = " ")
addScree(gp_pca)
abline(h = 1, col = "blue")

@@

```{r, gp-pca-direction, fig.cap="QoF disease register loadings on PC1 and PC2"}
ggbiplot(gp_pca, ellipse = TRUE, groups = gp_2020$hboard, obs.scale = 1, 
         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)

gp_2020 <- 
  gp_2020 %>% 
  left_join(bind_cols(practice_id = gp_2020$practice_id, gp_pca$x), 
            by = "practice_id") %>% 
  select(regional_unit = practice_id, everything(),
         -c(practiceid, county, cluster, postcode, lsoacode, easting, northing,
            chd:flu, PC4:PC18, year))
```

@@

gpMissing <- 
  function(data){
    data %>% 
      as_tibble() %>% 
      pivot_wider(id_cols = regional_unit, names_from = datename,
                  values_from = n, values_fill = NA) %>% 
      select(all_of(months), everything()) %>% 
      rowwise() %>% 
      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
      group_by(regional_unit) %>% 
      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
  }

missRemove <- 
  function(data){
    data %>% 
      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), 
                              TRUE, FALSE)) %>% 
      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE,
                                                FALSE)),
                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
  }

@@

full_data <- 
  data_files[c(1:10,12)] %>% 
  furrr::future_map(read_rds)

@@

n_practices %>% 
  left_join(missing_gp, by = "drug") %>% 
  left_join(missing_raw_data, by = "drug") %>% 
  left_join(poor_forcasts, by = "drug") %>% 
  mutate(drug = str_remove_all(drug, "ddd_"),
         drug = str_remove_all(drug, "quant_"),
         drug = str_remove_all(drug, "_ddd"),
         drug = relevel(as_factor(drug), ref = "all_drugs")) %>%
  rowwise() %>% 
  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
         total_removed = missing_gp + miss_either + mape_over_50, 
         n_rem = n - total_removed) %>% 
  knitr::kable(booktabs = TRUE, linesep = "", 
               col.names = c("drug", "n", "gp", "covid", "10_non_covid",
                             "either", "mape >50", "total", "remain"),
               caption = "Summary of GP practices removed for each drug.") %>% 
  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
           threeparttable = TRUE)
```

@@

## GEE results

```{r, gee-analysis, eval = FALSE}
ace <- 
  differences %>% 
  filter(drug == "ddd_ace") %>% 
  group_by(datename) %>% 
  slice(1:100, .preserve = TRUE) %>% 
  left_join(filter(gp, year == 2020), by = c("regional_unit" = "practice_id")) %>% 
  mutate(time_order = as.numeric(as.factor(datename)))

ace_gee <- geeglm(prop ~ wimd2019, data = ace, id = regional_unit, waves = time_order, corstr = "ar1")

summary(ace_gee)
```

@@

```{r, gls-functions}
#### Prep GLS data ####
glsData <- function(data){
  df <- 
    differences %>% 
    filter(drug == data) %>% 
    mutate(time_order = as.numeric(as.factor(datename)),
           pct_change = 100*(prop - 1)) %>% 
    select(c(regional_unit, time_order, pct_change))

  baseline <- subset(df, time_order == 2, -time_order)
  baseline <- upData(baseline, rename = c(pct_change = "prop0"), print = FALSE)
  followup <- subset(df, time_order > 2)
  both <- merge(baseline, followup, by = c("regional_unit"))

@@

#### GLS Analysis function ####
bestGLS <- function(data){
  cp <- list(corAR1, corExp, corCompSymm, corLin, corGaus, corSpher)
  z <- vector("list", length(cp))

  ### Fit models
  for(k in 1:length(cp)){
    z[[k]] <- gls(pct_change ~ dispensing + hboard + rcs(time_order, 4) + rcs(prop0, 4) + 
                    rcs(wimd2019, 4) + rcs(p_male, 4) + rcs(pm_65, 4) + 
                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + rcs(ngp, 4) + 
                    rcs(gp_load, 4),
                  data = data,
                  correlation = cp[[k]](form = ~time_order | regional_unit))
  }

  ### Select best model
  anova(z[[1]], z[[2]], z[[3]], z[[4]], z[[5]], z[[6]])
  best_model_aic <- 
    anova(z[[1]], z[[2]], z[[3]], z[[4]], z[[5]], z[[6]]) %>% 
    select(-call) %>% 
    tibble() %>% 
    arrange(AIC) %>% 
    head(1) %>% 
    .$Model

  ### Fit best model
  a <-  Gls(pct_change ~ dispensing + hboard + rcs(time_order, 4) + 
              rcs(prop0, 4) + rcs(wimd2019, 4) + rcs(p_male, 4) + rcs(pm_65, 4) +               rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4)+ rcs(ngp, 4) + 
                    rcs(gp_load, 4),
            data = data, B = 1000, 
            correlation = cp[[best_model_aic]](form = ~time_order | regional_unit))

  return(a)
}

#### GLS Assumption Checking ####
glsAssump <- function(model, data){
  data$resid <- r <- resid(model); data$fitted <- fitted(model)
  y1 <- ylab("Residuals")
  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point() + 
    facet_grid(~hboard) + y1
  p2 <- ggplot(data, aes(x = prop0, y = resid)) + geom_point() + y1
  p3 <- ggplot(data, aes(x = time_order, y = resid)) + y1 + 
    stat_summary(fun.data = "mean_sdl", geom = "smooth")
  p4 <- ggplot(data, aes(sample = resid)) + stat_qq() + 
    geom_abline(intercept = mean(r), slope = sd(r)) + y1

@@

#### GLS Estimated Effects ####
glsEffects <- function(model, name){
  p1 <- ggplot(Predict(model, time_order, dispensing, conf.int = FALSE),
               adj.subitle = FALSE, legend.position = "top", )
  p2 <- ggplot(Predict(model, prop0), adj.subtitle = FALSE)
  p3 <- ggplot(Predict(model, pm_65), adj.subtitle = FALSE)
  p4 <- ggplot(Predict(model, p_male), adj.subtitle = FALSE)
  p5 <- ggplot(Predict(model, wimd2019), adj.subtitle = FALSE)
  p6 <- ggplot(Predict(model, PC1), adj.subtitle = FALSE)
  p7 <- ggplot(Predict(model, PC2), adj.subtitle = FALSE)
  p8 <- ggplot(Predict(model, PC3), adj.subtitle = FALSE)
  p9 <- ggplot(Predict(model, hboard), adj.subtitle = FALSE)
  p10 <- ggplot(Predict(model, ngp), adj.subtitle = FALSE)
  p11 <- ggplot(Predict(model, gp_load), adj.subtitle = FALSE)
  gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2)
  gridExtra::grid.arrange(p5,p6,p7,p8, ncol = 2)
  gridExtra::grid.arrange(p9,p10,p11, ncol = 2)

  capture.output(print(model))[16:53] %>% 
    read_table(., col_names = c(" ", "Coef", "S.E.", "t", "Pr(>|t|)")) %>% 
    kable(booktabs = TRUE, linesep = "", digits = 2,
               caption = paste(name, "coefficents")) %>% 
    kable_styling(bootstrap_options = "striped") %>% 
    print()

  plot(anova(model))

  model %>% 
    anova() %>% 
    kable(booktabs = TRUE, linesep = "", digits = 2,
          caption = paste(name, "anova")) %>% 
    add_indent(positions = c(4,6,8,10,12,14,16,18,20,22)) %>% 
    kable_styling(bootstrap_options = "striped") %>% 
    print()

  # time_order and prop0 dominate so not useful
  # n <- nomogram(model, abbrev = TRUE)
  # plot(n, )
  cat("\n\n")
}

drugs <- unique(differences$drug)

gls_analysis_fig_cap <- 
  paste(paste(drugs, "assumptions"), paste(drugs, "effects1"), 
        paste(drugs, "effects2"), paste(drugs, "effects3"), 
        paste(drugs, "anova"), paste(drugs, "nomogram"))

gls_analysis_fig_cap <- NULL
for (i in 1:length(drugs)) {
  gls_analysis_fig_cap <- 
    c(gls_analysis_fig_cap, 
      paste(drugs[i], c("assumptions", "effects1", "effects2", "effects3",
                        "anova", "nomogram")))
}

>>>>

---
title: "Supplementary Information"
short_title: COVID-19 Prescribing
bibliography:
- r-references.bib
- ../references/library.bib
output:
  pdf_document: default

papersize: a4
header-includes:
  \usepackage{float}
  \let\origfigure\figure
  \let\endorigfigure\endfigure
  \renewenvironment{figure}[1][2] {
      \expandafter\origfigure\expandafter[H]
  } {
      \endorigfigure
  }

```{r setup, include = FALSE}
## Packages
# devtools::install_github("w-hardy/serCymruTools")
library(plyr); library(dplyr)
library(rms)
library(nlme)
library(tidyverse)
library(lubridate)
library(tsibble)
library(fable)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(knitr)
library(kableExtra)
library(papaja)
library(fuzzyjoin)
library(ggbiplot)

@@

## Data
gp <- 
  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid),
         hboard = case_when(hboard == "W11000023" ~ "BC",
                            hboard == "W11000024" ~ "P",
                            hboard == "W11000025" ~ "HD",
                            hboard == "W11000028" ~ "AB",
                            hboard == "W11000029" ~ "CaV",
                            hboard == "W11000030" ~ "CTM",
                            hboard == "W11000031" ~ "SB")) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  mutate(dispensing = case_when(tolower(dispensing) == "yes" ~ TRUE, 
                                tolower(dispensing) == "no" ~ FALSE),
         hboard = as.factor(hboard))

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data")) 
names(data_files) <- 
  str_remove_all(list.files("../data/prescribing_data"), ".rds")
pres_data <- 
  map(data_files, read_rds)

@@

# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE, 
                      echo = FALSE, fig.pos = 'h!')
kable_opts <- options(knitr.kable.NA = "-")
```

@@

```{r, gp-pca, fig.cap="Variance of QoF variables explained by individual principal components (lines) with cumulative proportion of variance explained (text)."}
#### Data ####
gp_2020 <- 
  filter(gp, year == 2020) %>% 
  rename(regional_unit = practice_id)

@@

#### Analysis ####
gp_pca <- 
  prcomp(select(gp_2020, c(chd:flu, p_fem, pm_65, pf_65)), center = TRUE, scale. = TRUE)

plot(gp_pca, type = "lines", main = " ", pch = 3)
addScree(gp_pca)
abline(h = 1, col = "blue")

gp_2020 <- 
  gp_2020 %>% 
  left_join(bind_cols(regional_unit = gp_2020$regional_unit, gp_pca$x), 
            by = "regional_unit") %>% 
  select(regional_unit = regional_unit, everything(),
         -c(practiceid, county, postcode, lsoacode, easting, northing,
            chd:flu, PC6:PC20, year))
```

```{r, gp-pca-direction, fig.cap=c("QoF disease register loadings on PC 1-2","QoF disease register loadings on PC 2-3","QoF disease register loadings on PC 3-4","QoF disease register loadings on PC 4-5")}
p1 <- ggbiplot(gp_pca, ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
      scale_colour_viridis_d(name = "Health board")
p2 <- ggbiplot(gp_pca, choices = 2:3,
         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
      scale_colour_viridis_d(name = "Health board")
p3 <- ggbiplot(gp_pca, choices = 3:4,
         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
      scale_colour_viridis_d(name = "Health board")
p4 <- ggbiplot(gp_pca, choices = 4:5,
         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
      scale_colour_viridis_d(name = "Health board")
p1
cat("\n\n")
p2
cat("\n\n")
p3
cat("\n\n")
p4
cat("\n\n")

@@

@@

gpMissing <- 
  function(data){
    data %>% 
      as_tibble() %>% 
      pivot_wider(id_cols = regional_unit, names_from = datename,
                  values_from = n, values_fill = NA) %>% 
      select(all_of(months), everything()) %>% 
      rowwise() %>% 
      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
      group_by(regional_unit) %>% 
      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
                miss_covid = sum(c_across(`2020 Jan`:`2020 Aug`))) %>% 
      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
      mutate(miss_10_non_covid = if_else(miss_non_covid >= 60/10, TRUE, FALSE))
  }

missRemove <- 
  function(data){
    data %>% 
      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), 
                              TRUE, FALSE)) %>% 
      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
                miss_10_non_covid = sum(if_else(miss_non_covid >= 60/10, TRUE,
                                                FALSE)),
                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
  }

@@

full_data <- 
  data_files[grep(pattern = "../data/prescribing_data/warfarin_ddd_nat.rds",
                x = data_files, value = FALSE, invert = TRUE)] %>% 
  furrr::future_map(read_rds)

@@

n_practices %>% 
  left_join(missing_gp, by = "drug") %>% 
  left_join(missing_raw_data, by = "drug") %>% 
  left_join(poor_forcasts, by = "drug") %>% 
  mutate(drug = str_remove_all(drug, "ddd_"),
         drug = str_remove_all(drug, "quant_"),
         drug = str_remove_all(drug, "_ddd"),
         drug = relevel(as_factor(drug), ref = "all_drugs")) %>%
  rowwise() %>% 
  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
         total_removed = missing_gp + miss_either + mape_over_50, 
         n_rem = n - total_removed) %>% 
  knitr::kable(booktabs = TRUE, linesep = "", 
               col.names = c("Drug", "n", "GP", "COVID", "10% non-COVID",
                             "Dispensing", "MAPE >50", "Total", "Remain"),
               caption = "Summary of GP practices removed for each drug.") %>% 
  kableExtra::add_header_above(c(" "= 2, "Missing" = 4, "Removed" = 2, " " = 1)) %>% 
  footnote(general = '"Dispensing" is not always equal to the sum of COVID and 10% non-COVID, as a single practice may be missing both data in covid months and more than 10% of data in the non-covid months, but will only be excluded once.',
           threeparttable = TRUE)

@@

```{r, oac-gen-trend, fig.cap="Warfarin as a percentage of all oral anticoagulant prescribing in Wales. Pink shading covers duration of Wales' \"stay at home\" order."}
read_rds("../data/prescribing_data/warfarin_ddd.rds") %>% 
  dplyr::group_by(datename) %>% 
  dplyr::summarise(quantity = median(quantity, na.rm = TRUE)) %>% 
  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
  ggplot(aes(x = datename)) + 
  geom_rect(aes(xmin = dmy("01-03-2020"), xmax = dmy("31-07-2020"), 
                ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0, alpha = 0.03) +
  geom_line(aes(y = quantity)) +
  geom_vline(aes(xintercept = dmy("01-03-2020")), lty = 2, col = "red") +
  scale_x_yearmonth() +
  xlab("Date") +
  ylab("Warfarin (percentage of all OACs)") +
  ylim(0, 100) # Dyfrig's request

@@

### Analysis

```{r, gls-functions}
drugs <- unique(differences$drug)

#### Prep GLS data ####
glsData <- function(data){
  df <- 
    differences %>% 
    filter(drug == data) %>% 
    mutate(Month = as.numeric(as.factor(datename)),
           pct_change = 100*(prop - 1)) %>% 
    select(c(regional_unit, Month, pct_change))

  baseline <- subset(df, Month == 2, -Month)
  baseline <- upData(baseline, rename = c(pct_change = "feb_diff"), print = FALSE)
  followup <- subset(df, Month > 2)
  both <- merge(baseline, followup, by = c("regional_unit"))

@@

#### Redundancy analysis model ####
redun <- list()
for(i in drugs){
  redun[[i]] <- redun(~hboard + dispensing + Month + feb_diff + wimd2019 + 
                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + gp_load,
                      data = glsData(i), r2 = .8, type = "adjusted") %>% 
    .$Out
}

# No redundent variables

#### GLS Analysis function ####
bestGLS <- function(data, bootstrap = FALSE){
  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
  z <- vector("list", length(cp))

  ### Fit models
  for(k in 1:length(cp)){
    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) +
                    hboard + dispensing +
                    rcs(wimd2019, 4) + 
                    rcs(ngp, 4) + rcs(gp_load, 4) + 
                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                    rcs(PC4, 4) + rcs(PC5, 4) +
                    hboard:rcs(Month, 4:7) +
                    dispensing:rcs(Month, 4:7) +
                    rcs(wimd2019, 4):rcs(Month, 4:7) +
                    rcs(ngp, 4):rcs(Month, 4:7) +
                    rcs(gp_load, 4):rcs(Month, 4:7),
                  data = data,
                  correlation = cp[[k]](form = ~ Month | regional_unit))
  }

  arma_tab <- # Table for p and q values for corARMA()
    tibble(p = 1:3, 
           q = rep(0,3)) %>% 
    mutate(model = row_number() + length(cp))

  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
                 .f = ~ if(.x > 0 | .y >0)
                 { # p = 0 & q = 0 fails
                   tryCatch(
                     {gls(pct_change ~ rcs(Month, 4:7) +
                            hboard + dispensing +
                            rcs(wimd2019, 4) + 
                            rcs(ngp, 4) + rcs(gp_load, 4) + 
                            rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                            rcs(PC4, 4) + rcs(PC5, 4) +
                            hboard:rcs(Month, 4:7) +
                            dispensing:rcs(Month, 4:7) +
                            rcs(wimd2019, 4):rcs(Month, 4:7) +
                            rcs(ngp, 4):rcs(Month, 4:7) +
                            rcs(gp_load, 4):rcs(Month, 4:7),
                          data = data,
                          correlation = corARMA(form = ~ Month|regional_unit, 
                                                p=.x, q=.y))
                     },
                     error = function(cond){
                       message(paste("Model causing error: p = ", 
                                     .x, "q = ", .y))
                       message("Original error message:")
                       message(cond)
                       return(NULL)
                     },
                     warning = function(cond){
                       message(paste("Model causing warning: p = ", 
                                     .x, "q = ", .y))
                       message("Original warning message:")
                       message(cond)
                       return(NULL)
                     }
                   )
                 }))

  ### Select best model
  names(z) <- paste0("model", 1:length(z))
  x <- z %>% 
    map(summary)

  # Get metrics for each model
  aic <- map_dfr(x, pluck("AIC"), .id = "model") 
  bic <- map_dfr(x, pluck("BIC"), .id = "model")
  log_lik <- map_dfr(x, pluck("logLik"), .id = "model")

  # Create table
  mod_comparison <- 
    bind_cols(metric = c("aic", "bic", "log_lik"), 
              bind_rows(aic,bic,log_lik)) %>% 
    pivot_longer(-metric) %>% 
    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
    rename(model = name) %>% 
    mutate(model = as.numeric(str_remove_all(model, "model")))

  # Select best model
  best_model_aic <- 
    mod_comparison %>% 
    arrange(aic, bic, desc(log_lik)) %>% 
    head(1) %>% 
    .$model

  ### Fit best model
  if(bootstrap == TRUE){  
    if(best_model_aic <= 6){
      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
                  hboard + dispensing +  
                  rcs(wimd2019, 4) + 
                  rcs(ngp, 4) + rcs(gp_load, 4) + 
                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                  rcs(PC4, 4) + rcs(PC5, 4) +
                  hboard:rcs(Month, 4:7) +
                  dispensing:rcs(Month, 4:7) +
                  rcs(wimd2019, 4):rcs(Month, 4:7) +
                  rcs(ngp, 4):rcs(Month, 4:7) +
                  rcs(gp_load, 4):rcs(Month, 4:7),
                data = data, B = 1000,
                correlation = 
                  cp[[best_model_aic]](form = ~ Month | regional_unit))
      }
    else{
      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
                  hboard + dispensing +  
                  rcs(wimd2019, 4) + 
                  rcs(ngp, 4) + rcs(gp_load, 4) + 
                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                  rcs(PC4, 4) + rcs(PC5, 4) +
                  hboard:rcs(Month, 4:7) +
                  dispensing:rcs(Month, 4:7) +
                  rcs(wimd2019, 4):rcs(Month, 4:7) +
                  rcs(ngp, 4):rcs(Month, 4:7) +
                  rcs(gp_load, 4):rcs(Month, 4:7),
                data = data, B = 1000,
                correlation = 
                  corARMA(form = ~ Month | regional_unit, 
                          p = filter(arma_tab, model == best_model_aic)$p, 
                          q = filter(arma_tab, model == best_model_aic)$q))
      }
  }
  else{
    if(best_model_aic <= 6){
      a <- Gls(pct_change ~ rcs(Month, 4:7) +
                 hboard + dispensing +  
                 rcs(wimd2019, 4) + 
                 rcs(ngp, 4) + rcs(gp_load, 4) + 
                 rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                 rcs(PC4, 4) + rcs(PC5, 4) +
                 hboard:rcs(Month, 4:7) +
                 dispensing:rcs(Month, 4:7) +
                 rcs(wimd2019, 4):rcs(Month, 4:7) +
                 rcs(ngp, 4):rcs(Month, 4:7) +
                 rcs(gp_load, 4):rcs(Month, 4:7),
               data = data,
               correlation = 
                 cp[[best_model_aic]](form = ~ Month | regional_unit))
    }
    else{
      a <- Gls(pct_change ~ rcs(Month, 4:7) +
                  hboard + dispensing +  
                  rcs(wimd2019, 4) + 
                  rcs(ngp, 4) + rcs(gp_load, 4) + 
                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
                  rcs(PC4, 4) + rcs(PC5, 4) +
                  hboard:rcs(Month, 4:7) +
                  dispensing:rcs(Month, 4:7) +
                  rcs(wimd2019, 4):rcs(Month, 4:7) +
                  rcs(ngp, 4):rcs(Month, 4:7) +
                  rcs(gp_load, 4):rcs(Month, 4:7),
               data = data,
               correlation = 
                 corARMA(form = ~ Month | regional_unit, 
                         p = filter(arma_tab, model == best_model_aic)$p, 
                         q = filter(arma_tab, model == best_model_aic)$q))
    }
  }
  return(a)
}

#### GLS Assumption Checking ####
glsAssump <- function(model, data){
  data$resid <- r <- resid(model); data$fitted <- fitted(model)
  y1 <- ylab("Residuals")
  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point(alpha = .1) + y1
  p2 <- ggplot(data, aes(x = feb_diff, y = resid)) + geom_point(alpha = .1) + y1
  p3 <- ggplot(data, aes(x = Month, y = resid)) + y1 + 
    stat_summary(fun.data = "mean_sdl", geom = "smooth")
  p4 <- ggplot(data, aes(sample = resid)) + stat_qq(alpha = .1) + 
    geom_abline(intercept = mean(r), slope = sd(r)) + y1

@@

#### GLS Estimated Effects ####
percentiles <- function(data, var){
  # return vector of 5th, 25th, 50th, 75th, and 95th percentile
  var <- enquo(var)
  data %>% 
    summarise(enframe(stats::quantile(!!var, c(.05, .25, .5, .75, .95)), 
                      "Percentile", "value"), .groups = "drop") %>% 
    mutate(value = round(value)) %>% .$value
}

# dodge <- position_dodge(width = .25)
predictPlot <- function(data = ., groups, names){
  groups <- enquo(groups)
  data %>% 
    tibble() %>% 
    group_by(Month, !!groups) %>% 
    summarise(yhat = mean(yhat)) %>% 
    mutate(groups = as.factor(!!groups)) %>% 
    ggplot(aes(x = Month, y = yhat, group = groups)) +
    geom_line(aes(col = groups)) +
    scale_colour_viridis_d(name = names) +
    scale_fill_viridis_d(name = names) +
    theme(legend.position = "top") +
    ylab(bquote(~X~hat(beta))) +
    ggthemes::theme_hc()
}

glsEffects <- function(model, name, data){

  Name <- case_when(name == "all_drugs" ~ "All",
                    name == "ace" ~ "ACEi",
                    name == "adreno" ~ "BAA",
                    name == "cortico" ~ "Inhaled \ncortico",
                    name == "hcq" ~ "HCQ",
                    name == "nsaid" ~ "NSAIDs",
                    name == "oral_contra" ~ "Oral\ncontra",
                    name == "paracet" ~ "Paracet",
                    name == "ssri" ~ "SSRIs",
                    name == "vitd" ~ "Vit D",
                    name == "warfarin" ~ "Warfarin")

  cat("\n\n")

  #### Plot interactions #### not including month*ngp as none significant
  p1 <- Predict(model, Month, dispensing, hboard, conf.int = .95) %>% 
    predictPlot(., groups = hboard, "Health board")
  gridExtra::grid.arrange(p1,nrow = 1, newpage = TRUE) # Effects 1
  cat("\n\n")

  p2 <- Predict(model, Month,  dispensing, hboard, conf.int = .95) %>% 
    predictPlot(., groups = dispensing, "Dispensing")
  gridExtra::grid.arrange(p2,nrow = 1, newpage = TRUE) # Effects 2
  cat("\n\n")

  p1 <- Predict(model, Month, dispensing, hboard,
                wimd2019 = percentiles(data, wimd2019),
                conf.int = .95) %>% 
        group_by(Month, wimd2019) %>% 
    summarise(yhat = mean(yhat)) %>% 
    predictPlot(., groups = wimd2019, "WIMD")
    gridExtra::grid.arrange(p1, nrow = 1, newpage = TRUE) # Effects 3
  cat("\n\n")

  p1 <- Predict(model, Month, dispensing, hboard,
                ngp = percentiles(data, ngp),
                conf.int = .95) %>% 
    predictPlot(., groups = ngp, "Number of GPs")
  gridExtra::grid.arrange(p1, ncol = 1, newpage = TRUE) # Effects 5
  cat("\n\n")

  p2 <- Predict(model, Month, dispensing, hboard,
                gp_load = percentiles(data, gp_load),
                conf.int = .95) %>% 
    predictPlot(., groups = gp_load, "GP load")
  gridExtra::grid.arrange(p2, nrow = 1, newpage = TRUE) # Effects 4
  cat("\n\n")

  p1 <- Predict(model, Month, dispensing, hboard,
                PC1 = percentiles(data, PC1),
                conf.int = .95) %>% 
    predictPlot(., groups = PC1, "PC1")
  p2 <- Predict(model, Month, dispensing, hboard,
                PC2 = percentiles(data, PC2),
                conf.int = .95) %>% 
    predictPlot(., groups = PC2, "PC2")
  p3 <- Predict(model, Month, dispensing, hboard,
                PC3 = percentiles(data, PC3),
                conf.int = .95) %>% 
    predictPlot(., groups = PC3, "PC3")
  p4 <- Predict(model, Month, dispensing, hboard,
                PC4 = percentiles(data, PC4),
                conf.int = .95) %>% 
    predictPlot(., groups = PC4, "PC4")
  gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2, newpage = TRUE) # Effects 6
  cat("\n\n")

  # #### ANOVA plot ####
  # p <- 
  #   capture.output(anova(model))[4:41] %>%
  #   read_fwf(fwf_empty(., col_names = c("Factor", "Chi-Square", "d.f.", "P"))) %>% 
  #   mutate(Factor = 
  #            str_remove_all(Factor, 
  #                           c(OPEN_PAREN %R% "Factor" %R% PLUS %R% 
  #                               "Higher Order Factors" %R% CLOSE_PAREN))) %>% 
  #   filter(!str_detect(Factor, "Nonlinear") &
  #            !str_detect(Factor, "TOTAL") &
  #            Factor != "All Interactions",
  #          !str_detect(Factor, c("f" %R% OPEN_PAREN %R% "A,B"))) %>% 
  #   ggplot(aes(x = `Chi-Square`-`d.f.`, 
  #              y = reorder(Factor, X = `Chi-Square`-`d.f.`))) +
  #   geom_point(aes(col = 
  #                    as.factor(if_else(as.numeric(str_remove_all(P, "<"))<.05, 
  #                                      TRUE,FALSE)))) +
  #   scale_color_discrete(name = "P < .05") + 
  #   xlab(expression(chi^2-"d.f.")) +
  #   ylab(NULL) +
  #   ggthemes::theme_few() 
  # 
  # gridExtra::grid.arrange(p, newpage = TRUE)
  # cat("\n\n")

  p <- anova(model, rm.other = list("Month"), trans = sqrt,
             tol = 1e-10, dec.chisq = 2, dec.p = 2) %>% 
    plot()

  p

  #### ANOVA Table ####
  # model %>% 
  #   anova() %>% 
  #   kable(booktabs = TRUE, linesep = "", digits = 2,
  #         caption = paste(Name, "Wald z-test statistics")) %>% 
  #   # add_indent(positions = c(3,5,6,8,10,11,13,15,17,19,21,23,25,27,28,30:34)) %>% 
  #   kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
  #   print()

  cat("\n\n")
}

gls_analysis_fig_cap <- NULL
for (i in 1:length(drugs)) {
  gls_analysis_fig_cap <- 
    c(gls_analysis_fig_cap, 
      paste(drugs[i], c("Assumptions", "Health board effects.", "Dispensing status effect.", "WIMD effects. Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Number of GPs effects. Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Patients per GP effects. Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Patient related variable principal components 1-4 effects. Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Relative importance of effects.")))
}
